### 2018-07-21 paper/design.tex
Renames global-overlay-design to spor

\begin{figure}[t]
  \centering
  \def\svgwidth{0.8\columnwidth}
  \import{figures/}{outline.pdf_tex}
  \caption{\label{fig:outline}%
    \commentDaniel{We must adapt this figure to the text.}
    Outline of \name's components. Users squads of devices are circled in gray. 
    From top to bottom: a user's devices collaborate through the Squad Overlay 
    (\cref{sec:squad_overlay}); online devices globally share information about 
    them to random peers (\cref{sec:global_overlay}); using the two above 
    overlays allows for the creation of \ac{SPOR} between sets of devices. 
    These protocols enables secure file transfer between users 
    (\cref{SPORES}).}
\end{figure}

@@

\include*{sphinxes}
\include*{global-overlay-design}
\include*{squad-overlay-design}
\include*{file-exchange-design}

>>>>

\begin{figure}[t]
  \centering
  \def\svgwidth{0.8\columnwidth}
  \import{figures/}{outline.pdf_tex}
  \caption{\label{fig:outline}%
    \commentDaniel{We must adapt this figure to the text.}
    Outline of \name's components. Users squads of devices are circled in gray. 
    From top to bottom: a user's devices collaborate through the Squad Overlay 
    (\cref{sec:squad_overlay}); online devices globally share information about 
    them to random peers (\cref{sec:SPOR}); using the two above 
    overlays allows for the creation of \ac{SPOR} between sets of devices. 
    These protocols enables secure file transfer between users 
    (\cref{SPORES}).}
\end{figure}

@@

\include*{sphinxes}
\include*{spor}
\include*{squad-overlay-design}
\include*{file-exchange-design}
